---
title       : Predicting Childrens' Height
subtitle    : Developing Data Products Deck
author      : JL
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview

This deck aims to research on the impact of parents' heights and children's gender on the children's heights.

--- .class #id 

## Source Data and Tools

Source Data: dataset GaltonFamilies in the HistData R package

Tools: shiny to build data product application and slidify to create decks

--- .class #id 

## Data

```{r}
library(HistData)
data(GaltonFamilies)
summary(GaltonFamilies)
```

--- .class #id 

## Model

```{r}
lm(childHeight ~ father + mother + gender, data=GaltonFamilies)
```

--- .class #id 

## Application

To show the impact of parents' height and children' gender, an application has been developed and deployed at https://jiayuliu.shinyapps.io/shiny_apps_1/.


--- .class #id 

